Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-27 paper.qmd
Updated Figure 17 axes positions
Reshape the axes

axes_obj <- gen_axes(
  data = scaled_pbmc_data, 
  proj_data = projected_df, 
  limits = 1)

@@

axes_obj <- gen_axes(
  data = scaled_mnist_data, 
  proj_data = projected_df, 
  limits = 1)

>>>>

axes_obj <- gen_axes(
  data = scaled_pbmc_data, 
  proj_data = projected_df,  
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75)

@@

axes_obj <- gen_axes(
  data = scaled_mnist_data, 
  proj_data = projected_df, 
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75)
